---
title: "PackageLab04"
author: 'Hamed&Omid'
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{linreg}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(PackageLab04)
```


In statistics, linear regression is a linear approach for modelling the
relationship between a scalar response and one or more explanatory
variables (also known as dependent and independent variables). The case
of one explanatory variable is called simple linear regression; for more
than one, the process is called multiple linear regression. This term is
distinct from multivariate linear regression, where multiple correlated
dependent variables are predicted, rather than a single scalar variable.

In this package we used Linear Regression and QR Decomposition for
calculations. Moreover, we created 5 methods in this package includes:

-   print()

-   plot()

-   resid()

-   pred()

-   coef()

-   summary()

You can find codes in sections bellow:

The first step is to calculate items such as betahat :

```{r 'linreg function'}

linreg <- function(formula , data) {
  
  # use model.matrix() to create the matrix X (independent variables)
  X <- model.matrix(formula,data)
  
  # pick out the dependent variable y using all.vars()
  y <- data[all.vars(formula)[1]]
  yy <- data[all.vars(formula)[1]]
  ## QR factorization
  QR <- qr(X)
  r <- QR$rank
  piv <- QR$pivot[1:r]
  
  ## estimate identifiable coefficients
  betahat <- solve.qr(QR, y)
  
  ## fitted values
  yhat <- as.vector(c(X[, piv] %*% betahat))
  y <-as.matrix( data[all.vars(formula)[1]])
  ## residuals
  resi <- as.vector(y - yhat)
  
  ## degree of freedom
  dof <- nrow(X) - r
  
  ## error variance
  se2 <- c(crossprod(resi)) / dof
  
  ## variance-covariance for coefficients
  v <- chol2inv(QR$qr, r) * se2
  
  ## t-value
  tval <- betahat / sqrt(diag(v))
  
  ## return
  return_obj <- list(Coefficients = betahat, fitted.values = yhat,
                     residuals = resi, degfreedom = dof,
                     vcov = v, varr = sqrt(se2), t_value = tval,call=match.call(), Y = yy)
  
  class(return_obj) <- 'linreg'
  return(return_obj)
  
}

```


The function above returns an object, therefore we should create an
object with this function:

```{r 'Create Object'}

mod_object <- linreg(Petal.Length~Species, data = iris)

```


Now, we have object 'mod_object' and we can create methods which
mentioned above:

```{r 'print'}

print.linreg <- function(obj){
  cat("Call:\n")
  print(obj$call)
  cat("\nCoefficients:\n")
  print(obj$Coefficients)
  
}
print(mod_object)

```


```{r 'plot'}

```


```{r 'resid'}

resid.linreg <- function(obj){
  return(obj$residuals)
  
}
resid(mod_object)

```


```{r 'pred'}

pred <- function(obj){
  return(obj$fitted.values)
  
}
pred(mod_object)

```


```{r 'coef'}

coef.linreg <- function(obj){
  names(obj$Coefficients)
  
  
}
coef(mod_object)

```


```{r 'summary'}

summary.linreg <- function(obj)
{
  se <- sqrt(diag(obj$vcov))
  tval <- obj$t_value
  TAB <- cbind(Estimate = obj$Coefficients,
               StdErr = se,
               t.value = tval,
               p.value = 2*pt(-abs(tval), df=obj$degfreedom))
  res <- list(call=obj$call,
              coefficients=TAB)
  class(res) <- "summary.linreg"
  print(res)
  cat("\nResidual standard error:" , obj$varr ,"on", obj$degfreedom ,"degrees of freedom")
}
summary(mod_object)

```